NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-06-26 paper/implementation.tex
grammar fix

\subsection{Implementation}
\label{sec:implementation}
The initial learning curve and workflow setup cost of the tool are often the most significant barriers for user adaptation.
In the proposed system, we approach these challenges by designing the system as a Python library rather than as a monolithic standalone application. 
Just like a Python plotting library, the different pieces of the visualization can be accessed individually, which helps ease the initial learning curve. 
The individual components can also be combined in any configuration desired by users via a simple Python API to better fit into one's workflow.
More importantly, the library-based design allows easy integration with the existing model implemented in Python.
%
To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction, accessing attention, to link the visualization to their NLP models (see the code example in \textbf{Appendix B}).

@@

%
In the proposed work, the NLI model is implemented in Python using \emph{pytorch}~\cite{PaszkeGrossChintala2017}.
The visual interface is implemented in Javascript using \emph{D3.js} library , and a Python server act as the glue between the Javascript visualization and the \emph{pytorch} model.

>>>>

\subsection{Implementation}
\label{sec:implementation}
The initial learning curve and workflow setup cost of the tool are often the most significant barriers for user adaptation.
In the proposed system, we approach these challenges by designing the system as a Python library rather than as a monolithic standalone application. 
Just like a Python plotting library, the different pieces of the visualization can be accessed individually, which helps ease the initial learning curve. 
The individual components can also be combined in any configuration desired by users via a simple Python API to better fit into one's workflow.
More importantly, the library-based design allows easy integration with the existing model implemented in Python.
%
To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction and accessing attention, to link the visualization to their NLP models (see the code example in \textbf{Appendix B}).

@@

%
In the proposed work, the NLI model is implemented in Python using \emph{pytorch}~\cite{PaszkeGrossChintala2017}.
The visual interface is implemented in Javascript using \emph{D3.js} library, and a Python server acts as the glue between the Javascript visualization and the \emph{pytorch} model.
